### 2021-07-21 IITD_Manuscript.tex
Initial commit

% arara: pdflatex
% arara: biber
% arara: pdflatex

\documentclass[12 pt]{article}

\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{gensymb}
\doublespacing
\usepackage{subfigure}
\usepackage{float}
%\usepackage{caption}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{romannum}

\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
\addbibresource{publishing.bib}
\usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
% \renewcommand{\finentrypunct}{
%   \addperiod\space
%   (Cited \arabic{citecounter}~time\ifnumequal{\value{citecounter}}{1}{}{s})%
%  }
\usepackage{hyperref}
%\graphicspath{{./graphics/}} % Add this if needed.

\setlength{\marginparwidth}{2cm}\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\addcitation}[1]{\todo[inline,color=green!40]{\textbf{Add citation: }#1}}
\newcommand{\adddiscussion}[1]{\todo[inline,color=blue!40!green]{\textbf{Add discussion: }#1}}
\newcommand{\adddata}[1]{\todo[inline,color=blue!60!green]{\textbf{Add data: }#1}}
\newcommand{\explain}[1]{\todo[inline,color=red!40!yellow]{\textbf{Explain: }#1}}
\newcommand{\reviewthis}[1]{\todo[color=yellow,inline]{\textbf{Review: }#1}}
\newcommand{\response}[3]{\todo[color=yellow!90!red,inline]{\textbf{Response to Reviewer #1 (comment #2): }#3}}
\newcommand{\rework}[1]{\todo[color=orange,inline]{\textbf{Rework: }#1}}
\newcommand{\incorrect}[1]{\todo[inline,color=red!70]{\textbf{Incorrect: }#1}}
\newcommand{\rephrase}[1]{\todo[inline,color=blue!40]{\textbf{Rephrase: }#1}}
\newcommand{\warning}[1]{\todo[color=red,inline]{\textbf{Warning: }#1}}
\newcommand{\modifyfigure}[1]{\todo[inline,color=yellow!80!blue]{\textbf{Modify figure: }#1}}
\newcommand{\pleaseconfirm}[1]{\todo[inline,color=red!80!blue]{\textbf{Please confirm: }#1}}
\newcommand{\query}[1]{\todo[color=gray,inline]{\textbf{Query: }#1}}
\newcommand{\missingacknowledgment}[1]{\todo[inline,color=red!80]{\textbf{Missing acknowledgment: }#1}}
\newcommand{\restructuredocument}[1]{\todo[inline,color=blue!80]{\textbf{Restructure document: }#1}}
\newcommand{\nice}[1]{\todo[color=green,inline]{\textbf{Nice: }#1}}
\newcommand{\done}[1]{\todo[inline,color=blue!10]{\textbf{Done: }#1}}
\newcommand{\reply}[1]{\todo[color=yellow!90!red,inline]{\textbf{Reply: }#1}}

\doublespacing

\title{Preparing a manuscript for a peer-reviewed journal the FMDL way}
\author[1]{\small First Author}
\author[2]{\small Second Author}
\author[1]{\small Third Author}
\author[1]{\small Postdoc Scholar}
\author[2]{\small Collaborating PI}
\author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}
\affil[1]{\footnotesize Functional Materials \& Devices Laboratory, Department of Electrical Engineering, IIT Delhi, New Delhi, NCT, India, 110 016.}
\affil[2]{\footnotesize Department of Chemistry, IIT Delhi, New Delhi, NCT, India, 110 016.}

\date{}
\begin{document}
\maketitle
\begin{abstract}
This is like a conference abstract, but shorter. No use of acronymns allowed. Briefly (one sentence), motivate the manuscript. Then say what you did. Finally, summarize the main result, including salient numbers from data. This will be the last part of the paper you write just before final grammar check. This will be the \textbf{\Huge \textcolor{red}{seventh}} part of the paper you write.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Read through the entire PDF. This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.

First some ground rules for labeling: sec for sections, fig for figures, tbl for tables.

This will be the \textbf{\Huge \textcolor{red}{sixth}} part of the paper you write.

Before you do anything here, you need to complete pre-writing:

\begin{enumerate}
\item Decide what is the story. Decide what are the figures.
\item What are sections needed? What are the key citations?
\item \textbf{You have not written a word yet at this stage. Just a sketch of the article on a piece of paper.}
\item Figures. Use .eps for vector graphics. Use .tiff for scan data.
\item Shared Zotero collection. Add all the key citations. Generate a .bib file.
\item Go for a walk. Think about your competition.
\item Prepare a competition table. List relevant parameters. Add needed references to Zotero collection.
\item Scribble out a flowchart for the argument flow.
\item Decide what are competing/contradictory references that a reviewer will ask about. Add them to Zotero.
\item Go for another walk. Decide if you can address any of the weaknesses in the paper now and how much time it will take. If you can do these quickly, go back to the step on figures (add/modify).
\end{enumerate}

The moment you complete the pre-writing process, clear a full day from all distractions (social media, email, phone, etc), and write the entire paper in 6 hours. This will take 2.5-3 hours if you are putting together a Letters type manuscript. Your actual numbers in practice will be about 15\% higher than these estimates for your first paper, with the measure improving as you gain more experience.

If you have more than one actively writing co-author, you both need to first share the Zotero collection. Then, depending on your preference, you can open a document on Google Docs, and set up a Zoom call while you co-write parts of the paper together in full markup simultaneously. Alternatively, you can push your part to GitHub and inform the other student/postdoc to do a git pull and proceed. If we are collaborating with a non-LaTeX using group, the Google Doc method might work better. The backup of using pandoc to convert back and forth always exists but that is more error prone.

First step in the paper is to proceed to the results section. Once you come back to this section do the following:

\begin{itemize}
\item Paragraph one should prove the importance of the topic of your study with citations to recent (last 3-5 years) literature, especially review articles.
\item Pararaph two should clearly establish the need statement for the study by clearly defining the open problem that needs addressing.
\item Paragraph three should very briefly tell the audience what you have done (abstract style) and which approach you have followed (if that is useful to include).
\end{itemize}

Once you have done the above, and also written up an abstract, it is now time to do the following:

\begin{enumerate}
\item Cutting: Prune your sentences to increase information density. Grammarly will also help, but the first part must be done by you.
\item Check for English\cite{burchfield:1998,strunk:2000}, and run it thoroughly through Grammarly.
\item Create a github repo. Under settings of the new repo, under notifications, add your email address, and mine. What this will do is that as soon as some changes are pushed, everyone gets notified. GitHub currently allows only two email addresses.
\item Commit the first verson and push.
\item We go back and forth. The more carefully you have written the first draft, the faster this process should go.
\item Format it for the target journal identified by both of us. At that point, send the draft out to all co-authors for comments. When a collaboration is involved, I will do this myself.
\item Run a Turnitin check - remember - no repositories.
\end{enumerate}

\section{Methods}
This will be the \textbf{\Huge \textcolor{red}{first}} part of the paper you write.

In this section, clearly describe how you did your work. Create subsections for materials analysis, device fabrication, device characterization etc. The description should tersely state (within parenthesis) what tools were used, along with OEM names. In case of software/computational work, you must clearly state the algorithm used, along with any software specialized tools. Do NOT mention LabVIEW, Matlab, Python, or any such general purpose tools - that looks amateurish. Any protocols used must be cited. Do not repeat yourself - if you have previously published with a given method, cite your previous work instead of writing everything again.

\section{Results}
\label{sec:results}

This will be the \textbf{\Huge \textcolor{red}{second}} part of the paper you write.

First insert figures (Fig.~(\ref{fig:cv})) and tables. Make sure that your figures use appropriate colors, fonts, etc. \cite{mcnames:2006}. Your sentences describing your data scientifically must appear in text, and must never use reference to figures or tables except inside parenthesis. Why? When we talk to each other, we do not speak out references, we speak out ideas. In that sense, cross references and citations are ``underspeak'' that are present in citations, or in parenthesis. This has the additional merit of saving you writing space.

\begin{figure}
\centering
\subfigure[Measured capacitance as a function of area.]{\label{fig:ca}\includegraphics[scale=0.2,keepaspectratio]{example-image-a}}
\subfigure[C(f) for different biases.]{\label{fig:cfv}\includegraphics[scale=0.2,keepaspectratio]{example-image-b}}
\caption{(a) Use clear images, preferably in .eps form for anything other than scan data, and (b) .png form for scan data.}
\label{fig:cv}
\end{figure}

\section{Discussion}
\label{sec:discussion}

This will be the \textbf{\Huge \textcolor{red}{fourth}} part of the paper you write. I have intentionally split it up because even in cases when this is not a separate section in your manuscript, you should write it after a break (writing acknowledgments) - there is a difference between a) what the data are, and b) what your data mean, in light of literature.

This section is often combined with Sec.~(\ref{sec:results}). Sometimes, it is important to have it separate, especially when a fair bit of data analysis and interpretation is involved, and you need to place the discussion of the results in context of the existing literature. Whether to split or not is a personal choice, but is largely driven by how much do your results need to be compared and/or contrasted with literature. Very often, a comparison table between this work, and other studies will be placed here.

This is also the place where you should criticize certain shortcomings of your own work. It is important to put that here to disarm overly critical reviewers.

\section{Conclusions}
\label{sec:conclusions}

This will be the \textbf{\Huge \textcolor{red}{fifth}} part of the paper you write. This serves as a precis of your discussion, but in terms of more pithy statements, and you should highlight what the results mean for the field. This is also the place where you talk about future work.

\section*{Acknowledgments}

This will be the \textbf{\Huge \textcolor{red}{third}} part of the paper you write. Immediately after you write about results, it should be easy to remember who helped you get those results.

FA and TA (PhD fellowships) and PS (postdoc fellowship) acknowledge support from Ministry of Human Resource \& Development (MHRD). SA acknowledges support from University Grants Commission. CP acknowledges partial support from grant XYZ from Department of Science \& Technology. PS and CA acknowledges support from grant ABC from Department of Science \& Technology. All authors acknowledge facility access to Central Research Facility (CRF) and Nanoscale Research Facility (NRF, NNetra program) at IIT Delhi. Authors acknowledge technical assistance from Mr. Did Occasional Measurements/Process Runs of CRF.

Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).

\printbibliography

\end{document}

### 2021-07-21 Writing_FMDL.tex
Initial commit

\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{For students who are struggling}
\author{Madhusudan Singh\thanks{Functional Materials \& Devices Laboratory}}
\date{June 2019}
\begin{document}

\maketitle

I am assuming that you have already set yourself up to work in the FMDL way with the README file in the repo. This document contains some helpful hints for students who might be struggling with putting together a draft. This is understandable - this may be the first time you have put together any serious document.

Publication, and scientific communication is central to the business of our corner of academics. You are likely reading this document as a first-year grad (MS or Ph. D.) student working in the general area of devices \& Materials. I am not going to go into the philosophy of writing an article, vital as it is, but will focus on operational choices that will get you up to speed as soon as possible.

Before we get started with the mechanics, if you are the kind of person who skims through instructions because you think that you are too good for clearly written instructions, then please stop reading this, clear out your desk if you have one, and find another advisor. If you can't or won't read, you do not have a future in research.

%Besides I have very little patience with people who waste my time because they cannot be bothered to read and follow instructions in matters such as these. Agreeing to advise you is a time-investment on my part. Putting together these instructions took time, If I find that your work ethic involves any variant of unprofessional \textit{dekh lenge chalta hai} nonsense, then spare us both the aggravation, and just leave. There are plenty of excellent and serious students who want to join, and make something of their lives, and you are just taking up space that does not belong to you.

If you are joining my lab as an engineering or sciences student without the benefit of an ICSE or comparable high school education, chances are that you have issues in clearly, conicsely and forcefully expressing yourself verbally and in the written form. This has possibly affected your confidence and made you think less of yourself. While these sentiments are understandable, they are without basis in reality. Lack of facility with expressing yourself does not make you a worse scientist, only an ineffective one. This handicap means that you may be great in the lab, but no one but your advisor (if that) will ever know that about you.

This is a (slowly) fixable problem. Please buy (or otherwise find) a copy of The Complete Sherlock Holmes: 2 Boxes Sets by Sir Arthur Conan Doyle (ISBN: 978-0553328257) from your favourite bookseller. Read this book for fun everyday, with no page targets. Don't let it interfere with your work, but use it for relaxation. It will take several months to undo the damage you have had to undergo in high school, but if you develop a habit of reading \textit{non-scientific} literature in your spare time, your command over English will get better.

\section{How to produce a manuscript suitable for editing and submission in the shortest possible time}

If you follow these instructions below, you will be able to \textbf{write} a defensible first draft of a manuscript in \textbf{six} hours. Of course, this assumes that your initial experiments are done, your figures are ready to go. Use the manuscript draft template in this repo - that has some more specific instructions.

\section{The soul of the paper: figures and arguments}

The root of the problem is sometimes some missing common sense, lack of seriousness, not being systematic.

Authoring of manuscripts. The editing process for a draft involves text changes, bibliography additions/deletions/changes, etc.

- The standard workflow for writing manuscripts is LaTeX/Zotero/Grammarly/TurnitIn/github. At least one complete cycle of this workflow should be executed before you send in the first draft. Your advisors are not your copy-editors, or plagiarism detectors, etc.

%- The standard section order as taught in ELV734/ELL834, is I-M-R-A-D-C-A. Introduction. Methods. Results & Discussion. Conclusions. Acknowledgments. This is so, regardless of the journal you are targeting. Even if it is a Letters journal without explicit sections.

- When you send me a draft, and it is not in the standard  workflow (such as rare cases where you are using Word), the bibliographic fields have to be editable. Not plain text. The same applies to Figure and Table cross-references. If you convert the fields to plain text, you are basically telling me that the number and ordering of the cross/references is sacrosanct, and will not be changed in editing. The slightest exertion of thinking would reveal that this is never the case, right until submission of the manuscript. For Word files, two files must always exist in your github repository - a) one draft with field codes active, b) one draft with field codes removed. The second file is what we submit. When stuff comes back for revisions, we edit a), and generate b).

- When you send me a draft that is written in broken glass form (sentences make little to no sense, methods are not described in process chronological order, stuff from different sections is mixed up, thoughts have no transition from one to the next, etc.), you are telling me that I do not have to take the manuscript seriously. I cannot possibly be more serious about your Ph. D. progress than you are. All you will accomplish with broken glass manuscripts is wasted time as I will just bounce it back to you, and develop a lower opinion of your level of commitment.

- Unsupported contentions. When matters of known facts are unreferenced, you are effectively claiming primacy over knowledge developed by others. This is one rung below plagiarism, and faces consequences that are nearly as severe. If you want a reviewer to give you really nasty report, by all means, continue with this unethical behaviour, and mess up your progress. No, supporting references are not sweet cherries that are distributed at the end. We remove unnecessary references at the end of the editing process, not add. Sentences in your draft and supporting references have to be added at the same time.

Authoring of presentations / posters.

- The attributions for figures (and less commonly, tables) take the following forms:
	a) (own work): everyone who helped you, as “Courtesy: X. Y. ZZZZ” in small red text. In case or NRF and CRF, it is “Courtesy: NRF/CRF”. If the measurement was done by a group colleague, it is “Courtesy: Mr. XYZ”, etc.
	b) (others’ work): citation in shortened form “Kim, et al, Appl. Phys. Lett., 2018” in small and red text.
	c) (own work, previously published), same as b, but with all last names, with your own name underlined.
	d) (own work, previously unpublished), same as c, but with current status of the publication listed (“In press”, “submitted”, etc.).
	e) (other’s work, uncited, discussion - this will be very rare), same as b) but with the journal name replaced with “Private communication”.

- The attributions when coupled with figures must appear in a group with the figure. That ensures that when you use builds, the attribution and the figure appear together at the same time. At no time should an unattributed piece of data be present on your slides during presentation. No, they are not going to wait for the next click.

\end{document}

### 2021-07-27 IITD_Manuscript.tex
Updated

@@
 Read through the entire PDF. This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.
-
-First some ground rules for labeling: sec for sections, fig for figures, tbl for tables.
 
@@
 
+The label in Fig.~(\ref{fig:cv}) is an example of a cross-reference.
+You \textbf{never} use absolute references in a document (like \verb|Fig.~1|).
+The reason for this ought to be obvious - while you author a text, things can move around, and you do not want to keep track of what moves where.
+\LaTeX\ is supposed to take care of that - not you.
+You can make mistakes, and mistakes can be costly.
+
+An equation can be similarly labelled:
+
+\begin{align}
+  E^{2} = p^{2} c^{2} + m_{0}^{2} c^{4} \label{eqn:relativistic4vector}
+\end{align}
+
+Not all equations need labels like Eq.~(\ref{eqn:relativistic4vector}) of course:
+
+\begin{align}
+  E & = h\nu \nonumber \\
+  & \equiv \frac{h c}{\lambda} \label{eqn:plancksrelationship}
+\end{align}
+
+In labeling (and referencing equations), be conservative.
+Label only those specific (and few) equations that you are actually going to use.
+Remember - any text can be made to look more inaccessible by involving more math.
+You should not show all steps in a paper, just the important ones that help you make your point.
+Needless to add, all your analytical calculations should be cross-checked with Maxima or Mathematica before it gets on your manuscript.
+
+Tables can be similarly cross-referenced as shown in Table~\ref{tbl:ratio}.
+
+\begin{table}
+  \caption{An example table}
+  \label{tbl:ratio}
+  \begin{center}
+    \begin{tabular}{cccccc}
+      x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
+      \hline \\
+         & (nm) & & K/A & Na/A & Nb/A \\
+      \hline \\
+      0.3 & 62 $\pm$ 4 & & 0.365 $\pm 2\%$ & 0.634 $\pm 2\%$ & 1.036 $\pm 2\%$ \\
+         & & & (0.3375) & (0.6624) & (1.028) \\
+      \hline \\
+      0.5 & 70 $\pm$ 2 & & 0.510 $\pm 2\%$ & 0.489 $\pm 2\%$ & 0.937 $\pm 2\%$ \\
+         & & & (0.5091) & (0.4910) & (1.037) \\
+      \hline \\
+      0.7 & 68 $\pm$ 2 & & 0.718 $\pm 2\%$ & 0.281 $\pm 2\%$ & 0.928 $\pm 2\%$ \\
+         & & & (0.7682) & (0.2317) & (1.153) \\
+      \hline \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Needless to add, you need to pick labels that reflect the contents of the object being referenced.
+
+Notice some ground rules for labeling: sec for sections, fig for figures, tbl for tables.
+This convention, that I follow in my documents, helps distinguish between the objects that are being referenced.
+It is for your own benefit of course.
+
 \section{Discussion}
@@
 CP acknowledges partial support from grant XYZ from Department of Science \& Technology.
-PS and CA acknowledges support from grant ABC from Department of Science \& Technology.
+PS and MS acknowledges support from grant ABC from Department of Science \& Technology.
 All authors acknowledge facility access to Central Research Facility (CRF) and Nanoscale Research Facility (NRF, NNetra program) at IIT Delhi.

### 2021-08-02 IITD_Manuscript.tex
Even clearer instructions regarding naming added.

@@
 
+% I am sorry to have to point this out, but you cannot make any changes to the PREAMBLE of this document.
+It is intentionally designed to keep things generic enough so that this manuscript can be subsequently reformatted to specific journal templates/class files with minimal fuss.
+For initial submissions, most journals will need just the PDF file (this format) for first round of review.
+If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it.
+Places in the preamble where you are allowed to make changes are explicitly marked with comments.
+
 \documentclass[12 pt]{article}
+% PREAMBLE starts here.
 
@@
 \usepackage{gensymb}
+\usepackage{physics}
 \doublespacing
@@
 \usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
-\addbibresource{publishing.bib}
+\addbibresource{publishing.bib} % Replace this with the name of your .bib file.
 \usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
@@
 \usepackage{hyperref}
-%\graphicspath{{./graphics/}} % Add this if needed.
+%\graphicspath{{./graphics/}} % Add this if needed. Replace graphics with Figures if that is the name of your folder.
 
@@
 
+% In the title, author and affil directives before, enter your details. Of course, the number of authors and affils can vary - comment out whatever you are not using/add more if needed.
+
 \title{Preparing a manuscript for a peer-reviewed journal the FMDL way}
-\author[1]{\small First Author}
-\author[2]{\small Second Author}
-\author[1]{\small Third Author}
-\author[1]{\small Postdoc Scholar}
-\author[2]{\small Collaborating PI}
-\author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}
-\affil[1]{\footnotesize Functional Materials \& Devices Laboratory, Department of Electrical Engineering, IIT Delhi, New Delhi, NCT, India, 110 016.}
-\affil[2]{\footnotesize Department of Chemistry, IIT Delhi, New Delhi, NCT, India, 110 016.}
+\author[1]{\small First Author} % ORCID ID of the first author
+\author[2]{\small Second Author}  % ORCID ID of the second author
+\author[1]{\small Third Author}  % ORCID ID of the third author
+\author[1]{\small Postdoc Scholar}  % ORCID ID of the postdoc involved
+\author[2]{\small Collaborating PI}  % ORCID ID of the collaborating PI
+\author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}  % ORCID ID: 0000-0001-5430-1405
+\affil[1]{\footnotesize Functional Materials \& Devices Laboratory, Department of Electrical Engineering, IIT Delhi, New Delhi, NCT, India, 110 016.} % Our lab - will remain untouched.
+\affil[2]{\footnotesize Department of Chemistry, IIT Delhi, New Delhi, NCT, India, 110 016.} % Change/comment out as needed
 
 \date{}
+
+% PREAMBLE ends here
+
 \begin{document}
@@
 \centering
-\subfigure[Measured capacitance as a function of area.]{\label{fig:ca}\includegraphics[scale=0.2,keepaspectratio]{example-image-a}}
-\subfigure[C(f) for different biases.]{\label{fig:cfv}\includegraphics[scale=0.2,keepaspectratio]{example-image-b}}
-\caption{(a) Use clear images, preferably in .eps form for anything other than scan data, and (b) .png form for scan data.}
+\subfigure[Measured capacitance as a function of area.]{\label{fig:ca}\includegraphics[width=88mm,keepaspectratio]{example-image-a}}
+\subfigure[C(f) for different biases.]{\label{fig:cfv}\includegraphics[width=88mm,keepaspectratio]{example-image-b}}
+\caption{(a) Use clear images, preferably in .eps form for anything other than scan data, and (b) .png form for scan data.
+The width of the figure is chosen to be 88mm since that is the typical width of a journal column in two-column format.
+Your figures must be clear to read easily at this size.
+If your figure is too wide to fit in this width, you can use the figure* environment, but that is done only in very rare cases where the figure is really complex.}
 \label{fig:cv}
@@
 You should not show all steps in a paper, just the important ones that help you make your point.
-Needless to add, all your analytical calculations should be cross-checked with Maxima or Mathematica before it gets on your manuscript.
+Needless to add, all your analytical calculations should be cross-checked with Maxima or Mathematica before it gets on your manuscript draft.
+No, you need to do that now.
+A neat trick in Mathematica is the use of \verb|TeXForm[]| function to output \LaTeX\ formatted code for the math.
+This may save you a lot of time, and transcription errors.
 
@@
 
+\begin{table}
+  \caption{An example table}
+  \label{tbl:ratio}
+  \begin{center}
+    \begin{tabular}{cccccc}
+      x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
+      \hline \\
+         & (nm) & & K/A & Na/A & Nb/A \\
+      \hline \\
+      0.3 & 62 $\pm$ 4 & & 0.365 $\pm 2\%$ & 0.634 $\pm 2\%$ & 1.036 $\pm 2\%$ \\
+         & & & (0.3375) & (0.6624) & (1.028) \\
+      \hline \\
+      0.5 & 70 $\pm$ 2 & & 0.510 $\pm 2\%$ & 0.489 $\pm 2\%$ & 0.937 $\pm 2\%$ \\
+         & & & (0.5091) & (0.4910) & (1.037) \\
+      \hline \\
+      0.7 & 68 $\pm$ 2 & & 0.718 $\pm 2\%$ & 0.281 $\pm 2\%$ & 0.928 $\pm 2\%$ \\
+         & & & (0.7682) & (0.2317) & (1.153) \\
+      \hline \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+\subsection{Naming things}
+
+There is an underlying philosophy to the way we do manuscripts in the lab - regardless of what it is, the name of the repo (already addressed in the README file), file, section, figure file, label to a figure, label to an equation, label to a table, etc.
+\textbf{\Huge \textcolor{red}{must reflect the contents of whatever is being referenced or named}}.
+Hopefully, Table~(\ref{tbl:namingthings}) will serve as a useful rolodex - it is not complete, but it is strongly indicative.
+
+\begin{center}
+  \begin{longtable}{|p{3cm}|p{5cm}|p{3.5cm}|p{2.5cm}|}
+    \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}\\
+    \hline
+    \textbf{Entity}  & \textbf{Purpose of the entity} &  \textbf{Good usage} & \textbf{Examples of poor choices} \\\hline
+    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyofparticle & Eq12, importantequation \\\hline
+    Label to a figure & To label a figure so that it can be used in a cross-reference & \textcolor{blue}{fig:}JVdata & Fig1 \\\hline
+    Label to a table & To label a table so that it can be used in a cross-reference & \textcolor{blue}{tbl:}ratio & Table1, reallyimportantsummary \\\hline
+    Label to a section & To label a section in the document so that it can be used in a cross-reference & \textcolor{blue}{sec:}discussion & Sec1 \\\hline
+    Name of a figure file & To name a figure file that can be subsequently called in includegraphics markup & JVdata.eps & Fig1b.eps, firstfigure.eps\\\hline
+    Name of the bibliography file & To name the .bib file that you will be using in this document & \textcolor{blue}{DOCNAME.bib} & references.bib \\\hline
+  \end{longtable}
+\end{center}
+
+It should be quite obvious why we follow the naming convention the way we do.
+If you choose to violate instructions provided in this document and the overall repo, please do us both the favor of not publishing.
+I do not care how good your science is, but if you cannot be bothered to use rational, common sense-based, \textbf{consistent and systematic} methods to communicate your science, you: a) are not a good scientist, and b) your communicated science will not make an impact anywhere.
+Good scientists are systematic, cautious, thorough, sceptical, thoughtful, and organized in a manner that makes machines look human by comparison.
+Yes, OCD is an occupational hazard in our business.
+Careful people show care and forethought in everything they can.
+
 \section{Conclusions}

### 2021-08-04 IITD_Manuscript.tex
Even clearer instructions regarding naming added.
Additional help for use of git added.
Updated acknowledgments with statement of contributions and CRediT taxonomy

@@
 
-Read through the entire PDF. This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.
+Read through the entire PDF.
+This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.
+You also need to pay attention to the comments in the .tex file associated with this PDF.
 
@@
 
-Needless to add, you need to pick labels that reflect the contents of the object being referenced.
-
-Notice some ground rules for labeling: sec for sections, fig for figures, tbl for tables.
-This convention, that I follow in my documents, helps distinguish between the objects that are being referenced.
-It is for your own benefit of course.
-
 \section{Discussion}
@@
 
-\begin{table}
-  \caption{An example table}
-  \label{tbl:ratio}
-  \begin{center}
-    \begin{tabular}{cccccc}
-      x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
-      \hline \\
-         & (nm) & & K/A & Na/A & Nb/A \\
-      \hline \\
-      0.3 & 62 $\pm$ 4 & & 0.365 $\pm 2\%$ & 0.634 $\pm 2\%$ & 1.036 $\pm 2\%$ \\
-         & & & (0.3375) & (0.6624) & (1.028) \\
-      \hline \\
-      0.5 & 70 $\pm$ 2 & & 0.510 $\pm 2\%$ & 0.489 $\pm 2\%$ & 0.937 $\pm 2\%$ \\
-         & & & (0.5091) & (0.4910) & (1.037) \\
-      \hline \\
-      0.7 & 68 $\pm$ 2 & & 0.718 $\pm 2\%$ & 0.281 $\pm 2\%$ & 0.928 $\pm 2\%$ \\
-         & & & (0.7682) & (0.2317) & (1.153) \\
-      \hline \\
-    \end{tabular}
-  \end{center}
-\end{table}
-
 \subsection{Naming things}
@@
 There is an underlying philosophy to the way we do manuscripts in the lab - regardless of what it is, the name of the repo (already addressed in the README file), file, section, figure file, label to a figure, label to an equation, label to a table, etc.
-\textbf{\Huge \textcolor{red}{must reflect the contents of whatever is being referenced or named}}.
+\textbf{\Huge \textcolor{blue}{must reflect the contents of whatever is being referenced or named}}.
 Hopefully, Table~(\ref{tbl:namingthings}) will serve as a useful rolodex - it is not complete, but it is strongly indicative.
@@
 \end{center}
+
+Needless to add, you need to pick labels that reflect the contents of the object being referenced.
+
+Notice some ground rules for labeling: sec for sections, fig for figures, tbl for tables.
+This convention, that I follow in my documents, helps distinguish between the objects that are being referenced.
+It is for your own benefit of course.
 
@@
 
+\subsection{Statement of contributions}
+
+FA fabricated the devices.
+FA and TA characterized devices.
+SA and PS synthesized active semiconductor materials.
+SA, TA, and PS carried out XPS measurements.
+FA, SA, TA, and PS carried out data reduction.
+FA, SA, PS, CP and MS carried out technical discussions.
+FA, SA, CP and MS wrote the manuscript.
+
+As per \href{https://casrai.org/credit/}{CRediT} taxonomy: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: CP and MS.
+
+\subsection{Conflicts of Interest}
 Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).

### 2021-08-04 IITD_Manuscript.tex
Updated acknowledgments with statement of contributions and CRediT taxonomy

--- 2021-08-02 IITD_Manuscript.tex
@@
 
+\subsection*{Statement of contributions}
+
+FA fabricated the devices.
+FA and TA characterized devices.
+SA and PS synthesized active semiconductor materials.
+SA, TA, and PS carried out XPS measurements.
+FA, SA, TA, and PS carried out data reduction.
+FA, SA, PS, CP and MS carried out technical discussions.
+FA, SA, CP and MS wrote the manuscript.
+
+As per \href{https://casrai.org/credit/}{CRediT} taxonomy: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: FA, CP and MS.
+
+\subsection*{Conflicts of Interest}
 Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).

### 2021-12-28 IITD_Manuscript.tex
Updated template in response to the latest submissions.

@@
 For initial submissions, most journals will need just the PDF file (this format) for first round of review.
-If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it.
+If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it, and discussing with me.
 Places in the preamble where you are allowed to make changes are explicitly marked with comments.
 
+% You must run your manuscript through Grammarly prior to sending me the first draft. Not doing so will only lead to waste of your time.
+
 \documentclass[12 pt]{article}
-% PREAMBLE starts here.
+% PREAMBLE starts here. You cannot make any changes until the PREAMBLE ends. It will be marked where it ends.
 
@@
 \usepackage{romannum}
+\usepackage{caption} % For Table of Contents entry
 
@@
 \usepackage{hyperref}
-%\graphicspath{{./graphics/}} % Add this if needed. Replace graphics with Figures if that is the name of your folder.
 
@@
 
-% In the title, author and affil directives before, enter your details. Of course, the number of authors and affils can vary - comment out whatever you are not using/add more if needed.
+% PREAMBLE ends here. You can make changes starting here.
+
+%\graphicspath{{./graphics/}} % Add this if needed. Replace graphics with Figures if that is the name of your folder.
+
+% In the title, author and affil directives before, enter your details.
+Of course, the number of authors and affils can vary - comment out whatever you are not using/add more if needed.
+Make sure you enter the ORCID ids for all authors in the comment after each listing below, after ':'.
 
 \title{Preparing a manuscript for a peer-reviewed journal the FMDL way}
-\author[1]{\small First Author} % ORCID ID of the first author
-\author[2]{\small Second Author}  % ORCID ID of the second author
-\author[1]{\small Third Author}  % ORCID ID of the third author
-\author[1]{\small Postdoc Scholar}  % ORCID ID of the postdoc involved
-\author[2]{\small Collaborating PI}  % ORCID ID of the collaborating PI
+\author[1]{\small First Author} % ORCID ID of the first author:
+\author[2]{\small Second Author}  % ORCID ID of the second author:
+\author[1]{\small Third Author}  % ORCID ID of the third author:
+\author[1]{\small Postdoc Scholar}  % ORCID ID of the postdoc involved:
+\author[2]{\small Collaborating PI}  % ORCID ID of the collaborating PI:
 \author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}  % ORCID ID: 0000-0001-5430-1405
@@
 \date{}
-
-% PREAMBLE ends here
 
@@
 
+\subsection*{Data availability}
+
+Authors will make data available upon reasonable request.
+
 \section*{Acknowledgments}
@@
 
-As per \href{https://casrai.org/credit/}{CRediT} taxonomy: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: FA, CP and MS.
+In terms of \href{https://casrai.org/credit/}{CRediT (Contributor Roles Taxonomy)}: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: FA, CP and MS.
 
@@
 
+\subsection*{Author Bios}
+
+% All author photos must be named as XYZbio.png where 'XYZ' are the disambiguated (see below) initials for each author.
+These must be saved where the rest of your graphics go - the figures subdirectory.
+% If you have never written a bio, see mine (below) for an idea of what to include.
+
+\begin{description}
+ \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{FA} is a new author when it comes to writing papers.
+He/she is slowly learning and will get much better with time.
+% FAbio.png goes here.
+You should replace the string 'FA' with your own initials.
+Keep the rest of the filename the same.
+If there is more than one author with the same initials, use 'FA1', 'FA2' etc.
+ \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{SA} is also a new author when it comes to writing papers.
+He/she is slowly learning and will get much better with time.
+% SAbio.png goes here.
+ \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{TA} is a somewhat seasoned author when it comes to writing papers.
+He/she is much than when he/she started.
+% TAbio.png goes here.
+ \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{PS} is quite experienced in writing papers.
+He/she is into teaching younger researchers in how to write a paper.
+% PSbio.png goes here.
+ \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{CP} is our honored colleague, without whose help this work would have never seen the light of the day.
+He/she is quite busy advising his/her own research group.
+% CPbio.png goes here.
+ \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{Madhusudan Singh} graduated at the top of his 5-year Integrated M.
+Sc.
+Physics class at IIT Kanpur in 1999 with minors in electrical engineering, and computer science.
+He earned his M.
+S.
+degrees in EE and in Mathematics in 2003 and Ph.
+D.
+(EE) in 2005 in transport in III-V nitride heterojunctions.
+After postdoctoral work at MIT in organic optoelectronics, he joined Arizona State University, where he developed printing technologies as a research scientist at the Flexible Display Center.
+After work on chalcogenide-based flexible electronics at the University of Texas at Dallas, and as an editor at Wiley, he joined the faculty of the Department of Electrical Engineering at IIT Delhi in 2013.
+His academic service has involved serving as a panel / proposal /application reviewer for the US National Science Foundation (NSF) and the US Department of Energy (DoE), Indian Science \& Engineering Research Board (SERB), Indo-US Science and Technology Forum (IUSSTF), as associate editor of Advanced Functional Materials, in addition to reviewing for several journals, and as editor for special issues for IEEE and IoP.
+His research interests lie in solution-processed and printed device fabrication methods, flexible electronics, materials and surface chemistry, low cost photovoltaics, solid-state lighting sources, and sensors and detectors.
+% No change.
+\end{description}
+
 \printbibliography
 
+\clearpage
+\section*{Table of Contents}
+
+% Most good journals require a table of contents entry (this is somewhat discipline and society dependent as well).
+The purpose of this is an advertisement for your article on the website of the journal.
+Ordinarily, this will be a separate document, but it is being included here as a separate section so that we can go through drafting of your article without worrying about edits in different files.
+
+\begin{figure*}[!h]
+\centering
+\includegraphics[width=130mm]{example-image-c}
+\captionsetup{labelformat=empty}
+\caption{A no more than a 30-words long sentence that summarizes what you did in this paper, written for the benefit of a technically-literate layperson.}
+\end{figure*}
+
 \end{document}

### 2022-03-15 ReviewerResponseWXYZ-N.tex
Addition of reviewer response template, and data/code/acceptance_iles/common/figures subdirectories

% Before you get started, replace "WXYZ-N" in the name of this file with the following string: where WXYZ are a four letter code for the journal (sometimes extractable from the reference code they assigned you after original submission - you can use our own (see below)). Examples:
% IEEE Sensors J: SENJ
% IEEE Sensors Letters: SENL
% physica status solid (A): PSSA
% MRS Advances: MRSA
% Applied Physics Letters: APLT
% J. Appl. Phys.: JAPS
% RSC Green Chemistry: RGRC
% Adv. Func. Mater: ADFM
% Adv. Mater.: ADMA
% MRS Communications: MRSC
% Phys. Rev. Lett.: PRLT
% Phys. Rev. B: PRVB

% N is the number of the review cycle you are in. If this is the first review report that we are responding to, N=1.

% So, for a review response to Advanced Functional Materials, where this is our second response to the reviewers, the name of the file should be ReviewerResponseADFM-2.tex

% We could have chosen to keep things simple and rely on GitHub to store old versions. The problem with that idea is that sometimes you need to cite/attach earlier responses in communications with journals, and it is more sensible to have an unmodified document on hand.

\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Required packages
\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{physics}
\doublespacing
\usepackage{subfigure}
\usepackage{float}
%\usepackage{caption}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{romannum}
\usepackage{caption} % For Table of Contents entry

\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
\addbibresource{publishing.bib} % Replace this with the name of your .bib file.
\usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
\DeclareSIUnit{\Molar}{M}
\DeclareSIPrefix\micro{\text{\textmu}}{-3}
\DeclareSIUnit\angstrom{\text {Å}}
\DeclareSIUnit\gauss{G}

\input{common/common} % To be commented out prior to submission.

% \renewcommand{\finentrypunct}{
%   \addperiod\space
%   (Cited \arabic{citecounter}~time\ifnumequal{\value{citecounter}}{1}{}{s})%
%  }
\usepackage{hyperref}
\graphicspath{{./figures/}}

\title{Response to reviewer comments \\
  \large \textsf{Title of your paper} (submission reference code from journal - typically a single alphanumeric string)}

\author[1]{\small First Author} % ORCID ID of the first author:
\author[2]{\small Second Author}  % ORCID ID of the second author:
\author[1]{\small Third Author}  % ORCID ID of the third author:
\author[1]{\small Postdoc Scholar}  % ORCID ID of the postdoc involved:
\author[2]{\small Collaborating PI}  % ORCID ID of the collaborating PI:
\author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}  % ORCID ID: 0000-0001-5430-1405
\affil[1]{\footnotesize Functional Materials \& Devices Laboratory, Department of Electrical Engineering, IIT Delhi, New Delhi, NCT, India, 110 016.} % Our lab - will remain untouched.
\affil[2]{\footnotesize Department of Chemistry, IIT Delhi, New Delhi, NCT, India, 110 016.} % Change/comment out as needed

\date{}
\begin{document}

\maketitle

We would like to thank the editor for arranging a careful review of this manuscript. We have gone through the reviewer comments in detail, and as requested, have carried out estimates of the obtained quantities after including corrections pointed out by the reviewers. We are thankful to the reviewers for their incisive and helpful comments.

Below, we list the changes made in response to reviewer comments and requests. The changes made have been incorporated in the manuscript as per requirements. The related figures has also been updated in the manuscript, if needed. For your convenience, a marked copy of the manuscript also submitted with changes in text and equations marked (red=deletion, blue=addition).

\textbf{Note to student}: No actual changes in the manuscript are supposed to be included below. Only their locations, and the reasoning/response are located in this document.

\textbf{Note to student}: No changes are marked up in the original document. The deletion (red) and addition (blue) markup is generated by my shell script that compares two checkpoints: a) last submission, b) pre-final draft and generates the difference tex file and pdf document automatically using git and latexdiff. Do not waste your time on marking up changes in the main document.

\begin{enumerate}
\item \textbf{Reviewer 1} % You can add as many items as needed below for this reviewer. Break up larger paragraphs into separate items which pertain to separate points. All text by the reviewer must be quoted in textit's, without \textbf{any} modifications. We are quoting the reviewer - it must be verbatim.
  \begin{enumerate}
  \item \textit{Comment 1 by reviewer 1.}

    Your response goes here. As shown in previous work\cite{goossens:1994}, the quantity A is expected to increase when parameter B is reduced. Our results are consistent with that. However, the reviewer's criticism that a different starting concentration could have been used to improve the S/N ratio is very helpful. Accordingly, we have repeated our measurements (results are in Fig.~4(c) of the main manuscript). The resulting changes have been summarized in Table~(\ref{tbl:discrepancy}).

    \begin{table}[!ht]
      \centering
      \caption{Summary of discrepancy from earlier submitted results. This table should not be in the main manuscript.}
      \label{tbl:discrepancy}
      \resizebox{10cm}{!}{%
        \begin{tabular}{ccc}
          \hline
          Frequency (\SI{}{\kilo\hertz}) & Original submission~$A$(\SI{}{\pico\meter\per\volt}) & Revised $A$(\SI{}{\pico\meter\per\volt}) \\
          \hline
          100 & 15.502 & 15.518  \\
          300 & 15.589 & 15.606  \\
          500 & 15.361 & 15.381  \\
          700 & 15.532 & 15.551  \\
          900 & 15.496 & 15.512  \\
          1000 & 15.442 & 15.459 \\
          \hline
        \end{tabular}}
    \end{table}

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 3, column 1, line 15: we have ...
    \item On page 4, column 2, line 2: we have ...
    \item Figure 4(c) has been updated with the new results.
    \item References [36] and [48] have been added to the manuscript.
    \end{itemize}

  \item \textit{Comment 2 by reviewer 1.}

    Your response goes here.

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 1, column 2, line 6: we have ...
    \item On page 5, column 1, line 20: we have ...
    \item Figure 2(b) has been updated with the new results.
    \item References [11] and [42] have been added to the manuscript.
    \end{itemize}
  \end{enumerate}

\item \textbf{Reviewer 2} % You can add as many items as needed below for this reviewer. Break up larger paragraphs into separate items which pertain to separate points. All text by the reviewer must be quoted in textit's, without \textbf{any} modifications. We are quoting the reviewer - it must be verbatim.
  \begin{enumerate}
  \item \textit{Comment 1 by reviewer 2.}

    Your response goes here.

    \begin{figure}
      \centering
      \includegraphics[width=88mm,keepaspectratio]{example-image-a}
      \caption{Use clear images, preferably in .eps form for anything other than scan data, and (b) .png form for scan data. The width of the figure is chosen to be 88mm since that is the typical width of a journal column in two-column format. This figure is meant \textbf{purely} for the reviewer's benefit - it is not included in the main manuscript. The need for use of this figure will be apparent from the nature of the comments.}
      \label{fig:cv}
    \end{figure}

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 3, column 1, line 15: we have ...
    \item On page 4, column 2, line 2: we have ...
    \item Figure 4(c) has been updated with the new results.
    \item References [36] and [48] have been added to the manuscript.
    \end{itemize}

  \item \textit{Comment 2 by reviewer 2.}

    Your response goes here.

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 1, column 2, line 6: we have ...
    \item On page 5, column 1, line 20: we have ...
    \item Figure 2(b) has been updated with the new results.
    \item References [11] and [42] have been added to the manuscript.
    \end{itemize}
  \end{enumerate}

\item \textbf{Reviewer 3} % You can add as many items as needed below for this reviewer. Break up larger paragraphs into separate items which pertain to separate points. All text by the reviewer must be quoted in textit's, without \textbf{any} modifications. We are quoting the reviewer - it must be verbatim.
  \begin{enumerate}
  \item \textit{Comment 1 by reviewer 3.}

    Your response goes here.

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 3, column 1, line 15: we have ...
    \item On page 4, column 2, line 2: we have ...
    \item Figure 4(c) has been updated with the new results.
    \item References [36] and [48] have been added to the manuscript.
    \end{itemize}

  \item \textit{Comment 2 by reviewer 3.}

    Your response goes here.

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 1, column 2, line 6: we have ...
    \item On page 5, column 1, line 20: we have ...
    \item Figure 2(b) has been updated with the new results.
    \item References [11] and [42] have been added to the manuscript.
    \end{itemize}
  \end{enumerate}

\end{enumerate}

We hope that the changes made in response to specific reviewer comments address their important concerns. We look forward to your further decision on this manuscript in this regard.

\textbf{Note to student}: Generally, once you have gone through 1-2 major revision / reject and resubmit decisions, the tone of the decision letter from the editor will make it clear whether they are hoping to accept the paper, or if they want production data. Some journals don't say anything in the decision letter, but during submission process, you have to provide production data for the publication process. The details of this vary from journal to journal. However, the source tex file (with the printbibliography replaced with the contents of the .bbl file), and high resolution figures are usually needed.  After preparing your reviewer response, it would be wise to provide these files under \verb|DOCNAME/acceptance_files| so that I do not have to harangue you for those files after we are ready to submit everything. There is a README file in that folder that tells you what to put where.

\printbibliography
\end{document}

### 2022-03-15 IITD_Manuscript.tex
Addition of reviewer response template, and data/code/acceptance_iles/common/figures subdirectories

@@
 It is intentionally designed to keep things generic enough so that this manuscript can be subsequently reformatted to specific journal templates/class files with minimal fuss.
-For initial submissions, most journals will need just the PDF file (this format) for first round of review.
-If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it, and discussing with me.
-Places in the preamble where you are allowed to make changes are explicitly marked with comments.
+For initial submissions, most journals will need just the PDF file (this format) for the first round of review.
+If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it and discussing it with me.
+Places in the preamble where you can make changes are explicitly marked with comments.
 
-% You must run your manuscript through Grammarly prior to sending me the first draft. Not doing so will only lead to waste of your time.
+% You must run your manuscript through Grammarly prior to sending me the first draft. Not doing so will only lead to an avoidable waste of your time.
 
@@
 \usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
+\DeclareSIUnit{\Molar}{M}
+\DeclareSIPrefix\micro{\text{\textmu}}{-3}
+\DeclareSIUnit\angstrom{\text {Å}}
+\DeclareSIUnit\gauss{G}
+
+\input{common/common} % To be commented out prior to submission.
+
 % \renewcommand{\finentrypunct}{
@@
 \usepackage{hyperref}
-
-\setlength{\marginparwidth}{2cm}\usepackage[colorinlistoftodos]{todonotes}
-\newcommand{\addcitation}[1]{\todo[inline,color=green!40]{\textbf{Add citation: }#1}}
-\newcommand{\adddiscussion}[1]{\todo[inline,color=blue!40!green]{\textbf{Add discussion: }#1}}
-\newcommand{\adddata}[1]{\todo[inline,color=blue!60!green]{\textbf{Add data: }#1}}
-\newcommand{\explain}[1]{\todo[inline,color=red!40!yellow]{\textbf{Explain: }#1}}
-\newcommand{\reviewthis}[1]{\todo[color=yellow,inline]{\textbf{Review: }#1}}
-\newcommand{\response}[3]{\todo[color=yellow!90!red,inline]{\textbf{Response to Reviewer #1 (comment #2): }#3}}
-\newcommand{\rework}[1]{\todo[color=orange,inline]{\textbf{Rework: }#1}}
-\newcommand{\incorrect}[1]{\todo[inline,color=red!70]{\textbf{Incorrect: }#1}}
-\newcommand{\rephrase}[1]{\todo[inline,color=blue!40]{\textbf{Rephrase: }#1}}
-\newcommand{\warning}[1]{\todo[color=red,inline]{\textbf{Warning: }#1}}
-\newcommand{\modifyfigure}[1]{\todo[inline,color=yellow!80!blue]{\textbf{Modify figure: }#1}}
-\newcommand{\pleaseconfirm}[1]{\todo[inline,color=red!80!blue]{\textbf{Please confirm: }#1}}
-\newcommand{\query}[1]{\todo[color=gray,inline]{\textbf{Query: }#1}}
-\newcommand{\missingacknowledgment}[1]{\todo[inline,color=red!80]{\textbf{Missing acknowledgment: }#1}}
-\newcommand{\restructuredocument}[1]{\todo[inline,color=blue!80]{\textbf{Restructure document: }#1}}
-\newcommand{\nice}[1]{\todo[color=green,inline]{\textbf{Nice: }#1}}
-\newcommand{\done}[1]{\todo[inline,color=blue!10]{\textbf{Done: }#1}}
-\newcommand{\reply}[1]{\todo[color=yellow!90!red,inline]{\textbf{Reply: }#1}}
-
-\doublespacing
+\graphicspath{{./figures/}}
 
@@
 
-%\graphicspath{{./graphics/}} % Add this if needed. Replace graphics with Figures if that is the name of your folder.
-
-% In the title, author and affil directives before, enter your details.
+% In the title, author, and affil directives before, enter your details.
 Of course, the number of authors and affils can vary - comment out whatever you are not using/add more if needed.
@@
 \begin{abstract}
-This is like a conference abstract, but shorter.
+This part is like a conference abstract, but shorter.
 No use of acronymns allowed.

### 2022-03-15 Writing_FMDL.tex
Addition of reviewer response template, and data/code/acceptance_iles/common/figures subdirectories

@@
 
-If you are joining my lab as an engineering or sciences student without the benefit of an ICSE or comparable high school education, chances are that you have issues in clearly, conicsely and forcefully expressing yourself verbally and in the written form.
+If you are joining my lab as an engineering or sciences student without the benefit of an ICSE or comparable high school education, chances are that you have issues in clearly, concisely and forcefully expressing yourself verbally and in the written form.
 This has possibly affected your confidence and made you think less of yourself.

### 2022-03-15 common/common.tex
Addition of reviewer response template, and data/code/acceptance_iles/common/figures subdirectories

\setlength{\marginparwidth}{2cm}\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\addcitation}[1]{\todo[inline,color=green!40]{\textbf{Add citation: }#1}}
\newcommand{\adddiscussion}[1]{\todo[inline,color=blue!40!green]{\textbf{Add discussion: }#1}}
\newcommand{\explain}[1]{\todo[inline,color=red!40!yellow]{\textbf{Explain: }#1}}
\newcommand{\reviewthis}[1]{\todo[color=yellow,inline]{\textbf{Review: }#1}}
\newcommand{\response}[3]{\todo[color=yellow!90!red,inline]{\textbf{Response to Reviewer #1 (comment #2): }#3}}
\newcommand{\rework}[1]{\todo[color=orange,inline]{\textbf{Rework: }#1}}
\newcommand{\incorrect}[1]{\todo[inline,color=red!70]{\textbf{Incorrect: }#1}}
\newcommand{\rephrase}[1]{\todo[inline,color=blue!40]{\textbf{Rephrase: }#1}}
\newcommand{\warning}[1]{\todo[color=red,inline]{\textbf{Warning: }#1}}
\newcommand{\modifyfigure}[1]{\todo[inline,color=yellow!80!blue]{\textbf{Modify figure: }#1}}
\newcommand{\pleaseconfirm}[1]{\todo[inline,color=red!80!blue]{\textbf{Please confirm: }#1}}
\newcommand{\query}[1]{\todo[color=gray,inline]{\textbf{Query: }#1}}
\newcommand{\missingacknowledgment}[1]{\todo[inline,color=red!80]{\textbf{Missing acknowledgment: }#1}}
\newcommand{\restructuredocument}[1]{\todo[inline,color=blue!50]{\textbf{Restructure document: }#1}} %The choice of color is very harsh on the eyes. Please keep it low.
\newcommand{\nice}[1]{\todo[color=green,inline]{\textbf{Nice: }#1}}
\newcommand{\done}[1]{\todo[inline,color=blue!10]{\textbf{Done: }#1}}
\newcommand{\reply}[1]{\todo[color=yellow!90!red,inline]{\textbf{Reply: }#1}}

### 2022-10-13 IITD_Manuscript.tex
Needed information added to template. Checkist added.

@@
 \usepackage{physics}
+\usepackage{array}
 \doublespacing
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{authblk}
@@
 \addbibresource{publishing.bib} % Replace this with the name of your .bib file.
-\usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
+\usepackage[separate-uncertainty = true,multi-part-units=single,per-mode=symbol]{siunitx}
 \DeclareSIUnit{\Molar}{M}
@@
 \DeclareSIUnit\gauss{G}
+\DeclareSIUnit\sq{\ensuremath{\Box}}
 
@@
 
+% Please enter information on potential reviewers below (at least 5, none from any of the co-author's affiliations, and none from IIT Delhi whatsoever.):
+% Reviewer 1: Name. Email address. Department. School/Company. Webpage URL. Reason for suggesting this reviewer.
+% Reviewer 2: Name. Email address. Department. School/Company. Webpage URL. Reason for suggesting this reviewer.
+% Reviewer 3: Name. Email address. Department. School/Company. Webpage URL. Reason for suggesting this reviewer.
+% Reviewer 4: Name. Email address. Department. School/Company. Webpage URL. Reason for suggesting this reviewer.
+% Reviewer 5: Name. Email address. Department. School/Company. Webpage URL. Reason for suggesting this reviewer.
+
 \date{}
@@
 \end{abstract}
+
+%%%%% DO-NOT-DELETE BLOCK STARTS %%%%
+
+\textcolor{purple}{\textsc{Checklist for you to follow before sending me the any draft (DO NOT DELETE until we are ready to submit this):
+\begin{enumerate}
+\item Have you read the \textbf{entire} README file in the manuscript repo?
+\item Have you read the PDF corresponding to this template file in the manuscript repo?
+\item Are your figures legible when reduced to 85 mm width in two column format?
+\item Have you ensured that the enumerate environment, if used in your manuscript, does not contain any absolute references?
+\item Have you ensured that you are using exactly zero absolute references when referring to figures, tables, etc.?
+If you see usage like "Fig.~(1)", I will refuse to entertain the manuscript any further.
+Lose any brain dead Microsoft Word habits you might have.
+\item Have you ensured that you are not using any figure placement modifiers like "h", "t", etc.
+Please lose any brain dead Microsoft Word habits you might have.
+\textbf{\LaTeX\ } decide where each figure will go.
+No, let it decide and get your meddling fingers away from document beautification and focus on the \textbf{content}.
+\item Does the shared Zotero collection under your shared collection contain all the citations in this manuscript?
+\item Has the shared Zotero collection been set to auto-export to the .bib file you added to the repo?
+\item Has this manuscript passed Grammarly with at least 99\% rating? The settings are described in the README in the manuscript repo.
+\item Have you increased the information density to the highest level possible using techniques I have taught you? This will involve a lot of cutting.
+\item Have you run Grammarly after doing the cutting, ensuring 99\% rating again?
+\item Has every deserving co-author been listed, and their ORCID id provided in comments in the \LaTeX\ source?
+\item Have you acknowledged everyone non co-author that helped you, under the acknowledgment section?
+\item Have you listed at least 5 potential reviewers for this manuscript above in comments in the \LaTeX\ source?
+\end{enumerate}
+}
+}
+
+%%%%% DO NOT DELETE BLOCK ENDS %%%%
 
@@
 \item \textbf{You have not written a word yet at this stage. Just a sketch of the article on a piece of paper.}
-\item Figures. Use .eps for vector graphics. Use .tiff for scan data.
+\item Figures.
+Use .eps for vector graphics.
+Use .tiff for scan data.
+For initial submission, please ensure that your figures do not exceed 1 MB in size or so.
+Scale down.
+You can use docupub to compress pdfs.
+High resolution images will be needed after acceptance of the manuscript.
 \item Shared Zotero collection. Add all the key citations. Generate a .bib file.
@@
 \item We go back and forth. The more carefully you have written the first draft, the faster this process should go.
-\item Format it for the target journal identified by both of us. At that point, send the draft out to all co-authors for comments. When a collaboration is involved, I will do this myself.
+\item Format it for the target journal identified by both of us.
+As soon as the decision regarding a journal has been made, go to that journal's website, and view the guide for authors on their webpage.
+There is usually a submission checklist document located under guide for authors which tells you what kind of documents are needed.
+Please create them all.
+\item Commit and push. I will view this draft and do some final checks, and prepare the cover letter.
+\item Once I push the updated version with the cover letter, and if no major changes are needed, send the draft out to all co-authors for comments.
+When a collaboration is involved, I will do this myself.
 \item Run a Turnitin check - remember - no repositories.
@@
 \clearpage
-\section*{Table of Contents}
+\section*{Graphical table of contents}
 
-% Most good journals require a table of contents entry (this is somewhat discipline and society dependent as well).
+% Most good journals require a graphical "table" of contents entry (this is somewhat discipline and society dependent as well).
 The purpose of this is an advertisement for your article on the website of the journal.

### 2022-11-18 IITD_Manuscript.tex
Updated checklist. Added workflow description in the conclusion section. Added patent templates.

@@
 \usepackage{gensymb}
-\usepackage{physics}
 \usepackage{array}
@@
 \addbibresource{publishing.bib} % Replace this with the name of your .bib file.
-\usepackage[separate-uncertainty = true,multi-part-units=single,per-mode=symbol]{siunitx}
+\usepackage[separate-uncertainty=true,multi-part-units=single,per-mode=symbol,range-units=single,range-phrase=\text{-}]{siunitx}
 \DeclareSIUnit{\Molar}{M}
-\DeclareSIPrefix\micro{\text{\textmu}}{-3}
-\DeclareSIUnit\angstrom{\text {Å}}
 \DeclareSIUnit\gauss{G}
 \DeclareSIUnit\sq{\ensuremath{\Box}}
+\DeclareSIUnit\degc{\unit{\degreeCelsius}}
 
@@
 \begin{enumerate}
+\item Are all physical quantities using siunitx like \qty{60}{\degreeCelsius}?
+\item Are all vendor sources mentioned in parenthesis at \textbf{FIRST} occurrence?
 \item Have you read the \textbf{entire} README file in the manuscript repo?
@@
 If you see usage like "Fig.~(1)", I will refuse to entertain the manuscript any further.
-Lose any brain dead Microsoft Word habits you might have.
-\item Have you ensured that you are not using any figure placement modifiers like "h", "t", etc.
-Please lose any brain dead Microsoft Word habits you might have.
-\textbf{\LaTeX\ } decide where each figure will go.
-No, let it decide and get your meddling fingers away from document beautification and focus on the \textbf{content}.
+Please rapidly lose any brain dead Microsoft Word habits you might have.
+\item Have you ensured that you are not using any figure placement modifiers like "h", "t", "H", etc.
+Let \textbf{\LaTeX\ } decide where each figure will go.
+\footnote{No - I do mean: let it decide and get your meddling fingers away from document beautification and focus on the \textbf{content}.
+And no, I do NOT care if the figure ends up a universe away from where you think it should go.
+You are a scientist in training.
+The day you decide to become a desktop publishing expert looking for a job in a graphic design house, we can discuss your Microsoft Word addiction more seriously.}
 \item Does the shared Zotero collection under your shared collection contain all the citations in this manuscript?
@@
 \item Has this manuscript passed Grammarly with at least 99\% rating? The settings are described in the README in the manuscript repo.
-\item Have you increased the information density to the highest level possible using techniques I have taught you? This will involve a lot of cutting.
+\item Have you increased the information density to the highest level possible using techniques I have taught you?
+This will involve a lot of cutting.
+This involves many devices I have taught you in the scientific writing class.
+An easy first one is to stop usage of the kind: "Fig X shows Y.".
+This statement is patronizing to the reviewer (he/she is capable of seeing this if you have made decent figures), and it wastes space.
+Better method: "TEM data (Fig.~ 2) suggests ...".
 \item Have you run Grammarly after doing the cutting, ensuring 99\% rating again?
@@
 
+Example text:
+
+Capacitance versus voltage characteristics was recorded using a low leakage probe station (EB mmW probe station, Everbeing) and semiconductor parameter analyzer (Keithley 4200-SCS), where both were connected using \SI{1.0}{meter} long triaxial cables (contributor to parasitic inductance and resistance).
+The force and sense terminals were connected in a dual connector configuration to enable sensitive measurement.
+
 \section{Results}
@@
 This has the additional merit of saving you writing space.
+
+The text must \textbf{not} contain any constructions of the sort: "X data is shown in Fig.~(Y)", or "Fig.~(Y) shows X data".
+Your reviewer is not blind.
+He/she can read.
+Patronizing the reviewer will not get you a positive decision.
 
@@
 
-An equation can be similarly labelled:
+An equation can be similarly labeled:
 
@@
 \end{align}
+, where $c$ is the speed of light in vacuum, $c$=\qty{2.99792458e8}{\meter\per\second}.
+Note that physical quantities must always be expressed using siunitx, and these can be used in text as well as math mode.
 
@@
 
+Overall sequence of operations in an edit cycle at our end:
+
+\begin{enumerate}
+\item You satisfy the checklist to the letter. Nothing is optional. If you have a doubt on how to satisfy a particular item, ask me.
+\item The above assumes that you have followed all the instructions above and in README.md in the manuscript repo.
+It is a long read.
+You will likely only need to do it once or twice in the time you are in my group.
+\item You push the first draft. I take a look at it once your number comes up in the queue. There may be other papers ahead of you in the queue.
+\item I leave comments for you to improve the manuscript.
+The first comments, if you have done a nice job, will be about the arguments you are making in the manuscript.
+If you not satisfied the checklist, I will be somewhat disgusted by the lack of application on display, and point out clerical issues in the checklist that were missed.
+What happens here is entirely in your control.
+\item You will work on the changes, and push this again, after going through the checklist.
+I will get to it when your manuscript comes to the top of my work queue.
+The number of times you get into the queue directly determines how long it takes for us to push the manuscript.
+Do a shoddy job, and we could be at it for a year.
+Do a good job, and it goes out in a week.
+It depends on your attention to detail, willingness to follow defined protocol, and level of seriousness and pride with which you approach your work.
+\item We will repeat the above a few times, depending on the number of clerical issues you have left unaddressed, length of the manuscript, and complexity of the arguments (which may need us to craft a very careful discussion section).
+\item Once I feel that the methods, results, discussion, conclusion and acknowledgment sections are written to my satisfaction, I will draft a cover letter.
+At this point, if there is any intellectual property that needs to be protected, we will carry out the following steps:
+
+  \begin{enumerate}
+  \item I will ask you to fill out the two forms on FITT website.
+These will be annexures A-1 and D: \href{https://fitt-iitd.in/wp-content/uploads/2020/05/Annex-A-1-Disclosure-form-for-registration-of-Provisional-Patent-at-IIT-Delhi.doc}{emergency provisional patent application}, and the \href{https://fitt-iitd.in/wp-content/uploads/2020/05/Annex-D-Disclosure-form-for-filing-a-Copyright-application-through-FITT.doc}{copyright application}.
+I have placed copies of these documents in the patent subfolder.
+Sorry - these are .odt files converted from .doc files copied from FITT website, so we will not be able to enjoy the advantages of fine-grained changes tracked by github.
+You will still do git add on the .odt files.
+  \item You will need to copy the introduction section from your draft, to the appropriate part of the forms above, and supply additional details\footnote{Please note that the language used in a patent application \textit{expands} potential application of your work to the maximum allowed by lawyers.
+The language used in the paper \textit{restricts} aspects of your work to the maximum we can support through citations to literature that fellow scientists will permit.
+The audiences for these documents are different: a) lawyers for the patents, b) scientists for the papers.}.
+  \item We will sign and submit the filing documents to FITT.
+They will go through initial due diligence, and get back to us.
+You will need to respond to their queries.
+Following this, the patent application will go to one of the lawyers retained by FITT, and discussions will take place on modifying the draft of the patent.
+  \end{enumerate}
+\item While the provisional patent application process is going on (this can take nearly a month), we will refine the Introduction section and write out a strong Conclusions section.
+Finally, we will write the abstract, and update the cover letter.
+The statement of contributions (CASRAI) and acknowledgments will need to be ready for review by co-authors at this point.
+The changes made will be committed and pushed.
+\item At this point, unless already decided, we will decide on the target journal.
+You will make needed changes to the format, and generate additional files needed by the target journal (details are available on their website).
+These may include: graphical abstract/Table of contents, highlights, any legal statement on copyright, etc.
+These changes will now be pushed.
+\item I will share the draft with our coauthors and collaborators, indicating the target journal, so that they can provide inputs.
+This may take a week.
+Once we receive feedback, we will update the draft, and push again.
+\item When the lawyers finally file the provisional patent, they will provide us with an application number.
+You will add a conflict of interest statement in the draft (see the section in this template) that mentions the application number.
+I will update the cover letter and add the same statement.
+\item We will submit the manuscript to the target journal, and await editorial decision.
+\item If the editorial decision is to reject the paper, we will reformat, inform co-authors, and resubmit it to an alternate journal. Otherwise, we will await the results of the first review cycle.
+\end{enumerate}
+
 \subsection*{Data availability}

### 2022-12-11 IITD_Manuscript.tex
Clarifications regarding writing and procedure regarding associated activities. Preamble reformat and instructions.

@@
 \documentclass[12 pt]{article}
-% PREAMBLE starts here. You cannot make any changes until the PREAMBLE ends. It will be marked where it ends.
 
-\usepackage[margin=1in,footskip=0.25in]{geometry}
-\usepackage{longtable}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage{textcomp}
-\usepackage{gensymb}
-\usepackage{array}
-\doublespacing
-\usepackage{subfigure}
-\usepackage{float}
-%\usepackage{caption}
-\usepackage[version=4]{mhchem}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{authblk}
-\usepackage{romannum}
-\usepackage{caption} % For Table of Contents entry
+%%% INSERT JOURNAL'S PREAMBLE HERE WHEN YOU ARE ASKED TO REFORMAT FOR AN IDENTIFIED TARGET JOURNAL
 
-\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
+%%% INSERT ENDS
+
+% PREAMBLE starts here.
+You cannot make any changes until the PREAMBLE ends.
+It will be marked where it ends.
+This must be commented out (and NOT deleted) when you reformat the manuscript for a target journal.
+
+\input{common/preamble} % To be commented out prior to reformatting for a target journal.
+\input{common/common} % To be commented out prior to submission.
 \addbibresource{publishing.bib} % Replace this with the name of your .bib file.
-\usepackage[separate-uncertainty=true,multi-part-units=single,per-mode=symbol,range-units=single,range-phrase=\text{-}]{siunitx}
-\DeclareSIUnit{\Molar}{M}
-\DeclareSIUnit\gauss{G}
-\DeclareSIUnit\sq{\ensuremath{\Box}}
-\DeclareSIUnit\degc{\unit{\degreeCelsius}}
-
-\input{common/common} % To be commented out prior to submission.
+This line will need to be commented out prior to reformatting for a journal, and replaced with a corresponding BibTeX directive (after re-exporting the .bib file with the changed format) since most journals still use BibTeX.
 
@@
 %  }
-\usepackage{hyperref}
+
 \graphicspath{{./figures/}}
 
-% PREAMBLE ends here. You can make changes starting here.
+% PREAMBLE ends here. You can make changes starting here, but changes are limited in scope.
 
@@
 Make sure you enter the ORCID ids for all authors in the comment after each listing below, after ':'.
-
+% WARNING: Do NOT delete this section even after you format it for a specific journal. Merely comment it out.
 \title{Preparing a manuscript for a peer-reviewed journal the FMDL way}
@@
 
-\date{}
+\date{} % Comment out prior to reformatting
+
+%%% INSERT JOURNAL SPECIFIC NON-PREAMBLE ITEMS LIKE FRONT PAGE STUFF, auth/affil blocks etc.
+
+%%% INSERT ENDS
 
 \begin{document}
-\maketitle
+\maketitle % You may have to comment this out when reformatting, unless the journal template also contains a reformatting command.
+
 \begin{abstract}
@@
 
-%%%%% DO-NOT-DELETE BLOCK STARTS %%%%
+\linenumbers % You may have to comment this out when reformatting, unless the journal requires that line numbers be placed in the text
 
-\textcolor{purple}{\textsc{Checklist for you to follow before sending me the any draft (DO NOT DELETE until we are ready to submit this):
-\begin{enumerate}
-\item Are all physical quantities using siunitx like \qty{60}{\degreeCelsius}?
-\item Are all vendor sources mentioned in parenthesis at \textbf{FIRST} occurrence?
-\item Have you read the \textbf{entire} README file in the manuscript repo?
-\item Have you read the PDF corresponding to this template file in the manuscript repo?
-\item Are your figures legible when reduced to 85 mm width in two column format?
-\item Have you ensured that the enumerate environment, if used in your manuscript, does not contain any absolute references?
-\item Have you ensured that you are using exactly zero absolute references when referring to figures, tables, etc.?
-If you see usage like "Fig.~(1)", I will refuse to entertain the manuscript any further.
-Please rapidly lose any brain dead Microsoft Word habits you might have.
-\item Have you ensured that you are not using any figure placement modifiers like "h", "t", "H", etc.
-Let \textbf{\LaTeX\ } decide where each figure will go.
-\footnote{No - I do mean: let it decide and get your meddling fingers away from document beautification and focus on the \textbf{content}.
-And no, I do NOT care if the figure ends up a universe away from where you think it should go.
-You are a scientist in training.
-The day you decide to become a desktop publishing expert looking for a job in a graphic design house, we can discuss your Microsoft Word addiction more seriously.}
-\item Does the shared Zotero collection under your shared collection contain all the citations in this manuscript?
-\item Has the shared Zotero collection been set to auto-export to the .bib file you added to the repo?
-\item Has this manuscript passed Grammarly with at least 99\% rating? The settings are described in the README in the manuscript repo.
-\item Have you increased the information density to the highest level possible using techniques I have taught you?
-This will involve a lot of cutting.
-This involves many devices I have taught you in the scientific writing class.
-An easy first one is to stop usage of the kind: "Fig X shows Y.".
-This statement is patronizing to the reviewer (he/she is capable of seeing this if you have made decent figures), and it wastes space.
-Better method: "TEM data (Fig.~ 2) suggests ...".
-\item Have you run Grammarly after doing the cutting, ensuring 99\% rating again?
-\item Has every deserving co-author been listed, and their ORCID id provided in comments in the \LaTeX\ source?
-\item Have you acknowledged everyone non co-author that helped you, under the acknowledgment section?
-\item Have you listed at least 5 potential reviewers for this manuscript above in comments in the \LaTeX\ source?
-\end{enumerate}
-}
-}
+\section{Prewriting}
 
-%%%%% DO NOT DELETE BLOCK ENDS %%%%
-
-\section{Introduction}
-\label{sec:introduction}
-
-Read through the entire PDF.
-This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.
-You also need to pay attention to the comments in the .tex file associated with this PDF.
-
-This will be the \textbf{\Huge \textcolor{red}{sixth}} part of the paper you write.
-
-Before you do anything here, you need to complete pre-writing:
+Before you do anything in this paper, you need to complete pre-writing:
 
@@
 
-The moment you complete the pre-writing process, clear a full day from all distractions (social media, email, phone, etc), and write the entire paper in 6 hours.
+The moment you complete the pre-writing process, \textbf{clear a full day} from all distractions (social media, email, phone, etc), and write the entire paper in 6 hours\footnote{If you have more than one actively writing co-author, you both need to first share the Zotero collection.
+Then, depending on your preference, you can open a document on Google Docs, and set up a Zoom call while you co-write parts of the paper together in full markup simultaneously.
+Alternatively, you can push your part to GitHub and inform the other student/postdoc to do a git pull and proceed.
+If we are collaborating with a non-\LaTeX\ using group, the Google Doc method might work better.
+The backup of using pandoc to convert back and forth always exists but that is more error prone.}.
 This will take 2.5-3 hours if you are putting together a Letters type manuscript.
@@
 
-If you have more than one actively writing co-author, you both need to first share the Zotero collection.
-Then, depending on your preference, you can open a document on Google Docs, and set up a Zoom call while you co-write parts of the paper together in full markup simultaneously.
-Alternatively, you can push your part to GitHub and inform the other student/postdoc to do a git pull and proceed.
-If we are collaborating with a non-LaTeX using group, the Google Doc method might work better.
-The backup of using pandoc to convert back and forth always exists but that is more error prone.
+\subsection{Sequence of writing the paper}
 
-First step in the paper is to proceed to the results section. Once you come back to this section do the following:
+The sequence of writing the sections (along with expected time taken in each part for a full research article):
+
+\begin{enumerate}
+\item (24 hours) Pre-writing (see above).
+\item (30 minutes) Methods
+\item (50 minutes) Results
+\item (20 minutes) Acknowledgments, which includes the statement of contributions, and conflicts of interest (such patent applications, etc.).
+\item (2.5 hours) Discussion.
+\item (20 minutes) Conclusions.
+\item (1 hour) Introduction (this section, see below).
+\item (30 minutes) Abstract.
+\end{enumerate}
+
+The sum of times above, after pre-writing, is 6 hours. If you are spending more time than is indicated above, you are not working with focus, or did not do a good job of pre-writing.
+
+\section{Introduction}
+\label{sec:introduction}
+
+Read through the entire PDF.
+This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.
+You also need to pay attention to the comments in the .tex file associated with this PDF.
+The pre-push checklist is listed in the appendix.
+
+Introduction will be the \textbf{\Huge \textcolor{red}{sixth}} part of the paper you write.
+First step in the paper is to proceed to the results section.
+Once you come back to this section do the following:
 
@@
 \section{Methods}
-This will be the \textbf{\Huge \textcolor{red}{first}} part of the paper you write.
+This will be the \textbf{\Huge \textcolor{red}{first}} part\footnote{This presumes that you have gone through the pre-writing phase.} of the paper you write.
 
@@
 The force and sense terminals were connected in a dual connector configuration to enable sensitive measurement.
+
+\subsection{Naming things}
+
+There is an underlying philosophy to the way we do manuscripts in the lab - regardless of what it is, the name of the repo (already addressed in the README file), file, section, figure file, label to a figure, label to an equation, label to a table, etc.
+\textbf{\Huge \textcolor{blue}{must reflect the contents of whatever is being referenced or named}}.
+Hopefully, Table~(\ref{tbl:namingthings}) will serve as a useful rolodex - it is not complete, but it is strongly indicative.
+
+\begin{center}
+  \begin{longtable}{p{3cm}p{5cm}p{3.5cm}p{2.5cm}}
+    \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}\\
+    \hline
+    \textbf{Entity}  & \textbf{Purpose of the entity} &  \textbf{Good usage} & \textbf{Examples of poor choices} \\\hline
+    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyofparticle & Eq12, importantequation \\\hline
+    Label to a figure & To label a figure so that it can be used in a cross-reference & \textcolor{blue}{fig:}JVdata & Fig1 \\\hline
+    Label to a table & To label a table so that it can be used in a cross-reference & \textcolor{blue}{tbl:}ratio & Table1, reallyimportantsummary \\\hline
+    Label to a section & To label a section in the document so that it can be used in a cross-reference & \textcolor{blue}{sec:}discussion & Sec1 \\\hline
+    Name of a figure file & To name a figure file that can be subsequently called in includegraphics markup & JVdata.eps & Fig1b.eps, firstfigure.eps\\\hline
+    Name of the bibliography file & To name the .bib file that you will be using in this document & \textcolor{blue}{DOCNAME.bib} & references.bib \\\hline
+  \end{longtable}
+\end{center}
+
+Needless to add, you need to pick labels that reflect the contents of the object being referenced.
+
+Notice some ground rules for labeling: sec for sections, fig for figures, tbl for tables.
+This convention, that I follow in my documents, helps distinguish between the objects that are being referenced.
+It is for your own benefit of course.
+
+It should be quite obvious why we follow the naming convention the way we do.
+If you choose to violate instructions provided in this document and the overall repo, please do us both the favor of not publishing.
+I do not care how good your science is, but if you cannot be bothered to use rational, common sense-based, \textbf{consistent and systematic} methods to communicate your science, you: a) are not a good scientist, and b) your communicated science will not make an impact anywhere.
+Good scientists are systematic, cautious, thorough, sceptical, thoughtful, and organized in a manner that makes machines look human by comparison.
+Yes, OCD is an occupational hazard in our business.
+Careful people show care and forethought in everything they can.
 
@@
       x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
-      \hline \\
          & (nm) & & K/A & Na/A & Nb/A \\
@@
 
+Do \textbf{NOT} patronize your reviewer by merely \textit{reading} the plots to them. That is \textbf{NOT} results or discussion.
+
 \section{Discussion}
@@
 
-This section is often combined with Sec.~(\ref{sec:results}).
-Sometimes, it is important to have it separate, especially when a fair bit of data analysis and interpretation is involved, and you need to place the discussion of the results in context of the existing literature.
+This is where analysis of your data in terms of a physical model, interpretation for various quantities in the model, or existing literature, etc.
+happens.
+Very often, the title of the article can change completely after a good discussion section.
+You can probably write a good discussion section provided you have a good idea of what the story of the paper is (from pre-writing).
+Conversely, a compelling analysis and discussion can better cement your ideas about what the story ought to be.
+The effect of this section permeates the entire paper.
+You will be writing the introduction section after writing the discussion section, and the conclusions.
+What kind of literature you cite will depend on what your story is turning out to be after analysis.
+
+This section is sometimes combined with Sec.~(\ref{sec:results}).
+Usually, it is important to have it separate, especially when a fair bit of data analysis and interpretation is involved, and you need to place the discussion of the results in context of the existing literature.
 Whether to split or not is a personal choice, but is largely driven by how much do your results need to be compared and/or contrasted with literature.
@@
 
-This is also the place where you should criticize certain shortcomings of your own work. It is important to put that here to disarm overly critical reviewers.
+Your target impact factor will be largely determined the quality of your discussion section.
 
-\subsection{Naming things}
-
-There is an underlying philosophy to the way we do manuscripts in the lab - regardless of what it is, the name of the repo (already addressed in the README file), file, section, figure file, label to a figure, label to an equation, label to a table, etc.
-\textbf{\Huge \textcolor{blue}{must reflect the contents of whatever is being referenced or named}}.
-Hopefully, Table~(\ref{tbl:namingthings}) will serve as a useful rolodex - it is not complete, but it is strongly indicative.
-
-\begin{center}
-  \begin{longtable}{|p{3cm}|p{5cm}|p{3.5cm}|p{2.5cm}|}
-    \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}\\
-    \hline
-    \textbf{Entity}  & \textbf{Purpose of the entity} &  \textbf{Good usage} & \textbf{Examples of poor choices} \\\hline
-    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyofparticle & Eq12, importantequation \\\hline
-    Label to a figure & To label a figure so that it can be used in a cross-reference & \textcolor{blue}{fig:}JVdata & Fig1 \\\hline
-    Label to a table & To label a table so that it can be used in a cross-reference & \textcolor{blue}{tbl:}ratio & Table1, reallyimportantsummary \\\hline
-    Label to a section & To label a section in the document so that it can be used in a cross-reference & \textcolor{blue}{sec:}discussion & Sec1 \\\hline
-    Name of a figure file & To name a figure file that can be subsequently called in includegraphics markup & JVdata.eps & Fig1b.eps, firstfigure.eps\\\hline
-    Name of the bibliography file & To name the .bib file that you will be using in this document & \textcolor{blue}{DOCNAME.bib} & references.bib \\\hline
-  \end{longtable}
-\end{center}
-
-Needless to add, you need to pick labels that reflect the contents of the object being referenced.
-
-Notice some ground rules for labeling: sec for sections, fig for figures, tbl for tables.
-This convention, that I follow in my documents, helps distinguish between the objects that are being referenced.
-It is for your own benefit of course.
-
-It should be quite obvious why we follow the naming convention the way we do.
-If you choose to violate instructions provided in this document and the overall repo, please do us both the favor of not publishing.
-I do not care how good your science is, but if you cannot be bothered to use rational, common sense-based, \textbf{consistent and systematic} methods to communicate your science, you: a) are not a good scientist, and b) your communicated science will not make an impact anywhere.
-Good scientists are systematic, cautious, thorough, sceptical, thoughtful, and organized in a manner that makes machines look human by comparison.
-Yes, OCD is an occupational hazard in our business.
-Careful people show care and forethought in everything they can.
+This is also the place where you should criticize certain shortcomings of your own work (typically towards the end), and indicate future work you may be doing to clear up open questions.
+It is important to put that here to disarm overly critical reviewers.
 
@@
 \item At this point, unless already decided, we will decide on the target journal.
-You will make needed changes to the format, and generate additional files needed by the target journal (details are available on their website).
+You will make needed changes to the format\footnote{However, you will not delete ANYTHING from the preamble.
+Comment out this template's preamble, auth/affil block, etc.
+and insert the journal's preamble in the section specifically marked in comments.}, and generate additional files needed by the target journal (details are available on their website).
 These may include: graphical abstract/Table of contents, highlights, any legal statement on copyright, etc.
@@
 
-This will be the \textbf{\Huge \textcolor{red}{third}} part of the paper you write. Immediately after you write about results, it should be easy to remember who helped you get those results.
+This will be the \textbf{\Huge \textcolor{red}{third}} part of the paper you write.
+Immediately after you write about results, it should be easy to remember who helped you get those results.
+This is also the right time to add the ORCID ids of all authors in the commented portion in the preamble.
 
@@
 \subsection*{Conflicts of Interest}
-Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).
+Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (201330070300).
 
-\subsection*{Author Bios}
+% \subsection*{Author Bios}
 
-% All author photos must be named as XYZbio.png where 'XYZ' are the disambiguated (see below) initials for each author.
+% This is included for completeness. Not all journals need this section. You can leave it commented out until the journal is finalized.
+
+% % All author photos must be named as XYZbio.png where 'XYZ' are the disambiguated (see below) initials for each author.
 These must be saved where the rest of your graphics go - the figures subdirectory.
-% If you have never written a bio, see mine (below) for an idea of what to include.
+% % If you have never written a bio, see mine (below) for an idea of what to include.
 
-\begin{description}
- \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{FA} is a new author when it comes to writing papers.
+% \begin{description}
+%  \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{FA} is a new author when it comes to writing papers.
 He/she is slowly learning and will get much better with time.
@@
 If there is more than one author with the same initials, use 'FA1', 'FA2' etc.
- \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{SA} is also a new author when it comes to writing papers.
+%  \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{SA} is also a new author when it comes to writing papers.
 He/she is slowly learning and will get much better with time.
 % SAbio.png goes here.
- \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{TA} is a somewhat seasoned author when it comes to writing papers.
+%  \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{TA} is a somewhat seasoned author when it comes to writing papers.
 He/she is much than when he/she started.
 % TAbio.png goes here.
- \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{PS} is quite experienced in writing papers.
+%  \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{PS} is quite experienced in writing papers.
 He/she is into teaching younger researchers in how to write a paper.
 % PSbio.png goes here.
- \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{CP} is our honored colleague, without whose help this work would have never seen the light of the day.
+%  \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{CP} is our honored colleague, without whose help this work would have never seen the light of the day.
 He/she is quite busy advising his/her own research group.
 % CPbio.png goes here.
- \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{Madhusudan Singh} graduated at the top of his 5-year Integrated M.
+%  \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{Madhusudan Singh} graduated at the top of his 5-year Integrated M.
 Sc.
@@
 % No change.
-\end{description}
+% \end{description}
 
@@
 \clearpage
+
+\appendix
+
+\section{Pre-push checklist}
+
+%%%%% DO-NOT-DELETE BLOCK STARTS %%%%
+\textcolor{purple}{%
+  \textsf{\small Checklist for you to follow before sending me the any draft (DO NOT DELETE until we are ready to submit this):
+    \begin{enumerate}
+    \item Please familiarize yourself with the accepted method of reporting measured data, and analytical/simulated quantities (\href{https://www.nist.gov/pml/special-publication-811/special-publication-811-extended-contents}{The NIST Guide for the user of the International System of Units: Special Publication 811}).
+    \item Are you following the rules governing reporting of data in terms of significant figures (see: \href{https://ccnmtl.columbia.edu/projects/mmt/frontiers/web/chapter_5/6665.html}{Significant Figures})?
+Chopping off or adding numbers to reported numbers for reasons of ``beautification'' are tantamount to malpractice, and almost as grievous as cooking up data.
+    \item Are all physical quantities using siunitx like \qty{60}{\degreeCelsius}?
+    \item Have you removed any patronizing comments to the reviewer by \textit{reading} your plots to him anywhere in the paper?
+You can cross-reference a plot, or specifically mention a number from such a plot, \textbf{if and only if} it allows you to make a scientific point in the discussion section.
+General comments like "test device performed measurably better than the control" can be mentioned in the results section, but only once, and that also in the last paragraph of your results section.
+    \item Are all vendor sources mentioned in parenthesis at \textbf{FIRST} occurrence?
+    \item Have you read the \textbf{entire} \href{https://github.com/FMDLab/manuscript\#readme}{README file} in the manuscript repo?
+    \item Have you read the PDF corresponding to this template file in the manuscript repo?
+    \item Are your figures legible when reduced to 85 mm width in two column format?
+    \item Have you ensured that the enumerate environment, if used in your manuscript, does not contain any absolute references?
+    \item Have you ensured that you are using exactly zero absolute references when referring to figures, tables, etc.?
+If you see usage like "Fig.~(1)", I will refuse to entertain the manuscript any further.
+Please rapidly lose any brain dead Microsoft Word habits you might have.
+    \item Have you ensured that you are not using any figure placement modifiers like "h", "t", "H", etc.
+Let \textbf{\LaTeX\ } decide where each figure will go.
+\footnote{No - I do mean: let it decide and get your meddling fingers away from document beautification and focus on the \textbf{content}.
+And no, I do NOT care if the figure ends up a universe away from where you think it should go.
+You are a scientist in training.
+The day you decide to become a desktop publishing expert looking for a job in a graphic design house, we can discuss your Microsoft Word addiction more seriously.}
+    \item Does the shared Zotero collection under your shared collection contain all the citations in this manuscript?
+    \item Has the shared Zotero collection been set to auto-export to the .bib file you added to the repo?
+    \item Has this manuscript passed Grammarly with at least 99\% rating? The settings are described in the README in the manuscript repo.
+    \item Have you increased the information density to the highest level possible using techniques I have taught you?
+This will involve a lot of cutting.
+This involves many devices I have taught you in the scientific writing class.
+An easy first one is to stop usage of the kind: "Fig X shows Y.".
+This statement is patronizing to the reviewer (he/she is capable of seeing this if you have made decent figures), and it wastes space.
+Better method: "TEM data (Fig.~ 2) suggests ...".
+    \item Have you run Grammarly after doing the cutting, ensuring 99\% rating again?
+    \item Has every deserving co-author been listed, and their ORCID id provided in comments in the \LaTeX\ source?
+    \item Have you acknowledged everyone non co-author that helped you, under the acknowledgment section?
+    \item Have you listed at least 5 potential reviewers for this manuscript above in comments in the \LaTeX\ source (in preamble)?
+    \end{enumerate}
+  }%
+}
+
+%%%%% DO NOT DELETE BLOCK ENDS %%%%
+
+\clearpage
+
 \section*{Graphical table of contents}

### 2022-12-11 common/preamble.tex
Clarifications regarding writing and procedure regarding associated activities. Preamble reformat and instructions.

\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{array}
\doublespacing
\usepackage{subfigure}
\usepackage{float}
%\usepackage{caption}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{romannum}
\usepackage{caption} % For Table of Contents entry
\usepackage{lineno}
\usepackage{booktabs}

\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
\usepackage[separate-uncertainty=true,multi-part-units=single,per-mode=symbol,range-units=single,range-phrase=\text{-}]{siunitx}
\DeclareSIUnit{\Molar}{M}
\DeclareSIUnit\gauss{G}
\DeclareSIUnit\sq{\ensuremath{\Box}}
\DeclareSIUnit\degc{\unit{\degreeCelsius}}
\usepackage{hyperref}

### 2023-02-22 ReviewerResponseWXYZ-N.tex
Updated checklist. Added workflow description in the conclusion section. Added patent templates.
Added tabularray. xr functionality still not fully worked out.

@@
 \usepackage{caption} % For Table of Contents entry
-
+\usepackage{xr} % For referencing portions of external documents, such as your main manuscript.
 \usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
@@
 \DeclareSIUnit\gauss{G}
+
+\externaldocument[main:]{IITD_Manuscript} % Replace this with the name of the file you are using for your main manuscript - you will be referencing locations in that file, by prefixing all references there with "main:".
+Citations can be handled the same way.
+You may have to "clean" all temporary files to make this work.
+See usage example below.
 
@@
 The changes made have been incorporated in the manuscript as per requirements.
-The related figures has also been updated in the manuscript, if needed.
+The related figures have also been updated in the manuscript, if needed.
 For your convenience, a marked copy of the manuscript also submitted with changes in text and equations marked (red=deletion, blue=addition).
@@
 \begin{enumerate}
-\item \textbf{Reviewer 1} % You can add as many items as needed below for this reviewer.
+\item \textbf{Reviewer 1} % \textit{You can add as many items as needed below for this reviewer.
 Break up larger paragraphs into separate items which pertain to separate points.
 All text by the reviewer must be quoted in textit's, without \textbf{any} modifications.
-We are quoting the reviewer - it must be verbatim.
+We are quoting the reviewer - it must be verbatim (not even a space bar or extra comma should be missing, even if there are grammatical or spellings errors).}
   \begin{enumerate}
@@
 
-    Your response goes here.
+    Response: Your response goes here.
 As shown in previous work\cite{goossens:1994}, the quantity A is expected to increase when parameter B is reduced.
@@
 
-    Your response goes here.
+    Response: Your response goes here.
 
@@
     \begin{itemize}
-    \item On page 1, column 2, line 6: we have ...
+    \item On page \pageref{main:page:rev1q2}, line \ref{main:line:rev1q2}: we have ...
     \item On page 5, column 1, line 20: we have ...
-    \item Figure 2(b) has been updated with the new results.
-    \item References [11] and [42] have been added to the manuscript.
+    \item Figure \ref{main:fig:revisedtem} has been updated with the new results.
+    \item References \cite{main:virtanen:2020}, \cite{main:perez:2011} and \cite{main:stancin:2019} have been added to the manuscript.
     \end{itemize}
@@
 
-\item \textbf{Reviewer 2} % You can add as many items as needed below for this reviewer.
+\item \textbf{Reviewer 2} % \textit{You can add as many items as needed below for this reviewer.
 Break up larger paragraphs into separate items which pertain to separate points.
 All text by the reviewer must be quoted in textit's, without \textbf{any} modifications.
-We are quoting the reviewer - it must be verbatim.
+We are quoting the reviewer - it must be verbatim.}
   \begin{enumerate}
@@
 
-\item \textbf{Reviewer 3} % You can add as many items as needed below for this reviewer.
+\item \textbf{Reviewer 3} % \textit{You can add as many items as needed below for this reviewer.
 Break up larger paragraphs into separate items which pertain to separate points.
 All text by the reviewer must be quoted in textit's, without \textbf{any} modifications.
-We are quoting the reviewer - it must be verbatim.
+We are quoting the reviewer - it must be verbatim.}
   \begin{enumerate}

### 2023-02-23 Rev_SolProc.tex
Initial commit. Blank manuscript

--- 2022-12-11 IITD_Manuscript.tex
@@
 
-\documentclass[12 pt]{article}
+\documentclass[12pt,twocolumn]{article}
 
@@
 
-\begin{center}
-  \begin{longtable}{p{3cm}p{5cm}p{3.5cm}p{2.5cm}}
-    \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}\\
+\scriptsize
+\begin{table}
+  \centering
+  \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}
+  \begin{tabular}{p{1.5cm}p{2.5cm}p{3cm}p{2cm}}
     \hline
     \textbf{Entity}  & \textbf{Purpose of the entity} &  \textbf{Good usage} & \textbf{Examples of poor choices} \\\hline
-    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyofparticle & Eq12, importantequation \\\hline
+    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyparticle & Eq12, importantequation \\\hline
     Label to a figure & To label a figure so that it can be used in a cross-reference & \textcolor{blue}{fig:}JVdata & Fig1 \\\hline
@@
     Name of the bibliography file & To name the .bib file that you will be using in this document & \textcolor{blue}{DOCNAME.bib} & references.bib \\\hline
-  \end{longtable}
-\end{center}
+  \end{tabular}
+\end{table}
+\normalsize
 
@@
   \centering
-\subfigure[Measured capacitance as a function of area.]{\label{fig:ca}\includegraphics[width=88mm,keepaspectratio]{example-image-a}}
-\subfigure[C(f) for different biases.]{\label{fig:cfv}\includegraphics[width=88mm,keepaspectratio]{example-image-b}}
-\caption{(a) Use clear images, preferably in .eps form for anything other than scan data, and (b) .png form for scan data.
-The width of the figure is chosen to be 88mm since that is the typical width of a journal column in two-column format.
+  \begin{subfigure}{80mm}
+    \centering
+    \includegraphics[width=\textwidth]{example-image-a}
+    \caption{Measured capacitance as a function of area.}
+    \label{fig:ca}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{80mm}
+    \centering
+    \includegraphics[width=\textwidth]{example-image-b}
+    \caption{C(f) for different biases.}
+    \label{fig:cfv}
+  \end{subfigure}
+  \caption{\subref{fig:ca} Use clear images, preferably in .eps form for anything other than scan data, and \subref{fig:cfv} .png form for scan data.
+The width of the figure is chosen to be 80mm since that is the typical width of a journal column in two-column format.
 Your figures must be clear to read easily at this size.
-If your figure is too wide to fit in this width, you can use the figure* environment, but that is done only in very rare cases where the figure is really complex.}
+If your figure is too wide to fit in this width, you can use the figure* environment, but that is done only in very rare cases where the figure is really complex.
+In case, we switch to using a large figure panel that cuts across two columns, each subfigure will need to be reduced to a width of around 40mm (for 2 in a row) or 27 cm (for 3 in a row), and so on.}
   \label{fig:cv}
@@
 \begin{table}
-  \caption{An example table}
+  \caption{An example table. The width of this table is controllable using p parameters instead of merely centering everything. For large tables, we may have to use both columns.}
   \label{tbl:ratio}
@@
 It is important to put that here to disarm overly critical reviewers.
+
+This part demonstrates how to add things here during revisions and how to correctly refer to them in the reviewer response document:
+
+\begin{figure}
+  \centering
+  \begin{subfigure}{42mm}
+    \centering
+    \includegraphics[width=\textwidth]{example-image-a}
+    \caption{High-resolution TEM data.}
+    \label{fig:hrtem}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{42mm}
+    \centering
+    \includegraphics[width=\textwidth]{example-image-b}
+    \caption{Percentage coverage (from SEM data).}
+    \label{fig:surfacecoverage}
+  \end{subfigure}
+  \caption{\subref{fig:hrtem} This could be a response to revisions requested by a reviewer.
+\subref{fig:surfacecoverage}  You can use the labels used here in the response document since we have used package xr there, and defined this manuscript file as the external document there.}
+  \label{fig:revisedtem}
+\end{figure}
+
+High-resolution TEM data and surface coverage extracted from SEM data (Fig.~(\ref{fig:revisedtem})) which was analyzed using SciPy\cite{virtanen:2020}, which is a Python\cite{perez:2011,stancin:2019} library used for such tasks.
+indicate that surface roughness cannot be a candidate explanation for the observed high leakage current in the device.
+Instead, charge storage in the disordered film may be released over time.
+This aspect will be studied in a forthcoming paper\label{page:rev1q2}\linelabel{line:rev1q2}.
 
